A sensor grid approach for large scale acoustic monitoring

### 2017-06-26 paper/article.tex
more int results

@@

To evaluate the impact of the frame rate on intelligibility two objective metrics are considered: the Coherence Speech Intelligibility Index\cite{kates2005} (CSII) and frequency-weighted segmental SNR\cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio. These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study. For this reason, a small-scale perceptual test is also conducted. We use a dataset of clean speech recordings comprised of 9 french sentences enunciated by 3 male and 3 female speakers. The recordings are encoded with analysis frame rates of 50~Hz, 16~Hz, 8~Hz and 4~Hz for a total of 216 audio excerpts. At each test iteration, a listener is presented with sentences and asked both to transcribe the utterances and rate the global intelligibility between 1 and 5. Each sentence is tested twice in order to palliate the reduced number of participants. The listening bias induced is attenuated by using the 9 sentences only once for the two lower and higher frame rates. Furthermore, the global order of examples as well as speakers are randomized. Nine subjects of ages ranging from 17 to 60 and with normal hearing capacity participated.\\

These metrics require a recovery of the time-domain signal. To do so, a linearly-scaled spectrogram from the band-focused representations is estimated. This estimation can be achieved by multiplying by the scaled transpose of the forward transformation matrix. A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}. Signal phase is approximated by either white noise spectrogram scaling or a Griffin \& Lim algorithm \cite{griffin1984}, and the signal is retrieved using concatenation or overlap-add. When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\

@@

Finally, objective intelligibility metrics are estimated for the studied parameters and compared to an informal perceptual evaluation \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}. Figures~\ref{fig:csii_tob_fps} and \ref{fig:fwsnrseg_tob_fps} shows both the CSII and fwSNRseg indicators for varying frames per second in analysis. Figure~\ref{fig:subj_int} presents the results of the preliminar perceptual test for the same setup. We acknowledge that it is surely biased by the reduced number of participants and scarcity of tested audio material. However, it is sufficient to judge the relevance of objective indicators in our conditions and study the intelligibility of fast acoustical measurements.\\

Perceptual test results are in accordance with the formulated concerns. First, phonems separation is mandatory in order to ensure intelligibility. This implies an analysis frame rate significantly larger than that of phonems in the considered language. Here we observe a limit of about 10~Hz corresponding to a duration of 100~ms, rendering the studied 8~Hz measurements inintelligible. Few words were understood correctly as a result of coincidentally adequate frame timings, ie. analysis frames matching phonem utterances for a short duration. Similarly, framing effects induced by the proposed processing scheme yielded errors for higher fps transcriptions and a globally lower comprehension as perceived by the subjects.\\

The CSII accounts for the spectrogram distance between clean and distorted audio at each point in time and frequency. This includes the phase, which we discard early in the representation step. The error induced by forward and inverse third-octave bands transformation as well as operations reducing data dimensionality further contribute to very high point-wise disparities. In fact, the signal is too distorted for the proposed SNR normalization to ensure CSII values in the 0-1 range. When compared to perceptual test results, the CSII shows no clear separation in the 10 frames per second neighbourhood. It is therefore not a good indicator in our conditions.\\

Alternatively, the frequency-weighted segmental SNR considers only spectrogram magnitudes. As a result, distance is generally lower and a more representative of the induced perceptual distortion. Nevertheless, the fwSNRseg still uses a point-wise comparison which is certainly too precise for the studied degradations. Its shape seems more accurate at higher frame rates where intelligibility is almost constant. The previously observed threshold is however absent as the curve present a smoother increase trend, and the difference between 8~Hz and 16~Hz is not significant enough to correlate with subjective measurements.\\

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{figures/subj_int.eps}
	\caption{Results of the perceptual intelligibility test with subjective normalized for visibility. A limit for intelligibility appears at around 10~Hz, corresponding to the average duration of a phonem.}
	\label{fig:subj_int}
\end{figure}
\section{Conclusion}

>>>>

\subsection{Inintelligibility} \label{sec:inintelligibility}

@@

To evaluate the impact of the frame rate on intelligibility a perceptual test and the evolution of two objective measures are considered. For the evaluation, a dataset of clean speech recordings made of 9 french sentences enunciated by 3 male and 3 female speakers. The recorded sentences are encoded using the proposed approach with analysis frame rates of 50~Hz, 16~Hz, 8~Hz and 4~Hz for a total of 216 audio excerpts. For the perceptual test, each subject is presented with sentences and asked both to transcribe the utterances and rate the global intelligibility between 1 and 5. Due to the low number of sentences, each sentence is tested twice for the same subject but under different encoding setting and speaker identity. 8 subjects of age ranging from 17 to 60 which reported normal hearing  participated to the listening test. The test was conducted using a Matlab interface displayed with a desktop computer and audio was played through Beyerdynamics DT 770 headphones. The output level was set by the experimenter at the same level for all subjects.

Concerning the objective measures, we computed the Coherence Speech Intelligibility Index \cite{kates2005} (CSII) and the frequency-weighted segmental SNR \cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio as those two indicators have been shown to correlate well with perceptual tests \cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study. \\

These metrics require an estimate of the time-domain signal. To do so, a linearly-scaled spectrogram from the band-focused representations is estimated. This estimation can be achieved by multiplying by the scaled transpose of the forward transformation matrix. A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}. Signal phase is approximated by either white noise spectrogram scaling or the Griffin \& Lim algorithm \cite{griffin1984}. The signal is then retrieved using concatenation or overlap-add. When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\

@@

Objective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}. Figures~\ref{fig:csii_tob_fps} and \ref{fig:fwsnrseg_tob_fps} shows both the CSII and fwSNRseg indicators for varying encoding frames per second. Figure~\ref{fig:subj_int} presents the results of the perceptual test for the same encoder's settings.

Perceptual test results confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility}. Phonemes separation is indeed mandatory in order to ensure good intelligibility of speech. This implies an analysis frame rate significantly larger than the phonemes rate the considered language. A limit of about 10~Hz corresponding to a frame duration of 100~ms is observed, as the studied 8~Hz setting is found to be almost completely inintelligible. Very few words are understood correctly. And we assume that the correctly identified words are a result of coincidentally adequate frame timings, \textit{i.e.} analysis frames matching the location of phoneme utterances for a short duration. Similarly, framing effects induced by the proposed processing scheme yielded errors for higher frame rates transcriptions and a globally lower perceptual intelligibility.\\

The CSII accounts for the spectrogram distance between clean and distorted audio at each point in time and frequency. This includes the phase, which we discard early in the representation step. The error induced by forward and inverse third-octave bands transformation as well as operations reducing data dimensionality further contribute to very high point-wise disparities. In fact, the signal is too distorted for the proposed SNR normalization to ensure CSII values in the 0-1 range. When compared to perceptual test results, the CSII shows no clear separation around 10 frames per second. It is therefore not a good indicator in our conditions.\\

More interestingly, the frequency-weighted segmental SNR considers only spectrogram magnitudes. As a result, distance is generally lower and more representative of the induced perceptual distortion. Nevertheless, the fwSNRseg still uses a point-wise comparison which is certainly too precise for the level of degradations considered in this study. Indeed, it seems more accurate at higher frame rates compared to the results achieved using the perceptual test. Though, the threshold observed in the results of the perceptual test is not measured using the fwSNRseg metric and the difference between 8~Hz and 16~Hz is not large enough to match subjective measurements.\\

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{figures/subj_int.eps}
	\caption{Results of the perceptual intelligibility test with subjective normalized for visibility. A limit for intelligibility appears at around 10~Hz, corresponding to the average duration of a phoneme.}
	\label{fig:subj_int}
\end{figure}

\section{Conclusion}
